%Greg and Fred's NSF Grant Nov 2017
\documentclass[11pt]{NSFamsart}
\usepackage{latexsym,amsfonts,amsmath,epsfig,multirow,stackrel,natbib,tabularx,enumitem,xspace}

% This package prints the labels in the margin
%\usepackage[notref,notcite]{showkeys}


%\pagestyle{empty}
\thispagestyle{plain}
\pagestyle{plain}

\headsep-0.6in
%\headsep-0.45in

\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\textheight9in
%\textheight9.1in



%\setcounter{page}{1}


\begin{document}
%\setlength{\leftmargini}{2.5ex}

\centerline{\textbf{\Large Data Management Plan}}

\bigskip



This plan will make certain that the data produced during the period of this project is appropriately managed to ensure its usability, access and preservation.  The data produced by the proposed project will consist of theory, numerical software, and potential coursework. 

The PI, Co-PI, and participants in this project will publish the results of their theoretical, and 
computational investigations as early as appropriate in the form of peer-reviewed journal articles, 
conference abstracts and talks at various conferences and institutions. Authorship will accurately 
reflect the contributions of those involved.  Students will be particularly encouraged to publish their 
work. When allowed by publishers, pre-prints of publications will be posted on arXiv.

Most software resulting from this project will fall within the scope of the Guaranteed Automatic 
Integration Library (GAIL) and will become part of future public releases.  GAIL will be hosted on 
Github or a similar accessible repository as it is now.  It will be publicized through colloquium and 
conference talks and e-newsletters such as the NA-Digest.

Substantial software resulting from this project that does not fit within GAIL will likewise be 
published in an accessible repository.

In the spirit of reproducible research, the code used for numerical tests and figures for our 
publications will be included in the GAIL and other repositories.

We will fully comply with all applicable guidelines and policies on model and data sharing as mandated or recommended by NSF.

This Data Management Plan addresses NSF’s policy on the dissemination and sharing of research results within a reasonable time.  In accordance with this policy, this plan does not include preliminary analyses (including raw data), drafts of scientific papers, plans for future research, peer reviews, or communications with colleagues. 



\end{document}
