%Greg and Fred's NSF Grant Dec 2014
\documentclass[11pt]{NSFamsart}
\usepackage{latexsym,amsfonts,amsmath,epsfig,multirow,stackrel,natbib,tabularx,hyperref,enumitem,xspace}
\usepackage[dvipsnames]{xcolor}
% This package prints the labels in the margin
%\usepackage[notref,notcite]{showkeys}


%\pagestyle{empty}
\thispagestyle{plain}
\pagestyle{plain}

\headsep-0.6in
%\headsep-0.45in

\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\textheight9in
%\textheight9.1in
\newcommand\myshade{85}
\colorlet{mylinkcolor}{violet}
\colorlet{mycitecolor}{Aquamarine}
%\colorlet{mycitecolor}{OliveGreen}
\colorlet{myurlcolor}{YellowOrange}

\hypersetup{
	linkcolor  = mylinkcolor!\myshade!black,
	citecolor  = mycitecolor!\myshade!black,
	urlcolor   = myurlcolor!\myshade!black,
	colorlinks = true,
}



%\setcounter{page}{1}


\begin{document}
%\setlength{\leftmargini}{2.5ex}

\centerline{\textbf{\Large Facilities, Equipment and Other Resources}}

\bigskip

Sou-Cheng Terrya Choi, the co-PI will join the regular GAIL team meetings, in addition to working 
remotely.  She is employed full-time outside academia, but contributes to the project on a volunteer 
basis.  No salary is requested for her, but her travel related to the project will be supported.

All Illinois Tech faculty, PhD students, and visitors have offices provided at Illinois Tech.  Summer 
MS, BS, and high school students have shared work areas.  In addition to faculty, student and visitor 
offices and conference rooms provided by the Department of Applied Mathematics, the Center for 
Interdisciplinary Scientific Computation (CISC) also has office and meeting space available for use 
by this project.

The Department of Applied Mathematics has a research computer room that is available to all 
members of our department.  CISC has a 256-core cluster named von Neumann funded by the 
College of Science.  An increase in the number of cores within the year is likely. Von Neumann is 
available available to all Illinois Tech research faculty and is
centrally managed by Illinois Tech Office of Technology (OTS) Services.  Illinois Tech is connected 
to the \href{https://www.opensciencegrid.org}{Open Science Grid} through its own GridIIT.  

Illinois Tech has site licenses for Mathematica, MATLAB, SAS, and JMP.  Other open source 
software is also installed in our research and teaching laboratories.

Illinois Tech's university library provides access to journals, research monographs, and 
databases, either on-site, online or via inter-library loan.

Illinois Tech was listed on the National Federal Register of Historic Places in 2005. The proposed 
research activities will not make any physical changes to Illinois Tech's campus and buildings.





\end{document}
